Examining a Quarter Century of Publishing Trends in Social Work Research:

### 2015-04-03 manuscript.Rmd
Major cleanup. All functional.

---
title: "Examining a Quarter Century of Publishing Trends in Social Work Research: A Data Science Perspective"
author: 
output: pdf_document
---

@@

```{r imageMaker, comment=NA, echo=FALSE, eval=FALSE}
# Read data files
#load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
#load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
#hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)

#source("/Users/beperron/Git/SocialWorkResearch/functions/appendData.R")
#source("/Users/beperron/Git/SocialWorkResearch/functions/shortArticles.R")
#source("/Users/beperron/Git/SocialWorkResearch/functions/titleMatching.R")
#source("/Users/beperron/Git/SocialWorkResearch/functions/otherDocuments.R")
#source("/Users/beperron/Git/SocialWorkResearch/functions/titleMatching.R")
#source("/Users/beperron/Git/SocialWorkResearch/functions/fewArticles.R")
#source("/Users/beperron/Git/SocialWorkResearch/functions/pretty.R")

#appendData.f()
#shortArticles.f()
#titleMatching.f()
#otherDocuments.f()
#fewArticles.f()
#save.image(file = "socialWorkHistory.Rdata")
```

```{r methodSummaryData, eval=TRUE}
append.articles <- length(which(full.append.df$attributes == "article"))
append.journals <- filter(full.append.df, attributes == "journal") %>% 
    summarise(Unique = n_distinct(record))

@@

In 2012, the NIH established the Big Data to Knowledge (BD2K) initiative, recognizing the potential of data to advance our understanding of human health and disease.  This initiative was designed to support four broad goals:  1) to facilitate use of biomedical digital assets by making them discoverable, accessible, and citable; 2) to conduct research and develop methods, software and tools to analyze biomedical big data; 3) to enhance training in the development of use and tools necessary for biomedical big data science; and 4) to support a data ecosystem that accelerates discovery as part of the digital enterprise (NIH).  At roughly the same time, the National Science Foundation (NSF) created new initiatives to harness the potential of the data revolution, arguing that ”data are motivating a profound transformation in the culture and conduct of scientific research in every field of science and engineering ... American scientists must rise to the challenges and seize the opportunities afforded by this new, data-driven revolution" (Suresh, XXX).  The programs of the NSF are organized around capacity building and innovative applications.  Capacity building activities focus on developing fundamental theories, techniques, methodologies and technologies that are broadly applicable to big data problems.  Innovative applications relate to specific domains advancing innovative ideas that provide solutions “with potential for a broader impact on data science and its applications.”

@@

Many journals from allied health disciplines used one of the supplemental search terms in special editions, which were also included in the journal title.  Thus, many non-social work journals were captured in the extraction process.  To resolve this issue, we created a list of all journal titles that were not part of the core list defined by Hodge and Lacasse (2011).  Study authors reviewed these journal titles and discussed whether each candidate title should be retained or excluded.  When disagreements occurred, the study authors reviewed the mission and aims of the journals, names of editorial board members, and focus of the articles.  A consensus was reached on all journal titles to be excluded and retained.   After these procedures, the number of article records and journal titles was reduced to `r pretty(append.articles)` and `r append.journals` (respectively).

>>>>

---
title: 'Examining a Quarter Century of Publishing Trends in Social Work Research:
  A Data Science Perspective'
author: ''
output: pdf_document
---

@@

```{r imageMaker, comment=NA, echo=FALSE, eval=FALSE}
# Read data files
load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)

source("/Users/beperron/Git/SocialWorkResearch/functions/combineData.R")
source("/Users/beperron/Git/SocialWorkResearch/functions/cleaningJournals.R")
source("/Users/beperron/Git/SocialWorkResearch/functions/shortArticles.R")
source("/Users/beperron/Git/SocialWorkResearch/functions/titleMatching.R")
source("/Users/beperron/Git/SocialWorkResearch/functions/otherDocuments.R")
source("/Users/beperron/Git/SocialWorkResearch/functions/fewArticles.R")
source("/Users/beperron/Git/SocialWorkResearch/functions/pretty.R")

combineData.f()
cleaningJournals.f()
shortArticles.f()
titleMatching.f()
otherDocuments.f()
fewArticles.f()
#save.image(file = "socialWorkHistory.Rdata")
```

```{r methodSummaryData, eval=TRUE}
#append.articles <- length(which(full.append.df$attributes == "article"))
#append.journals <- filter(full.append.df, attributes == "journal") %>% 
#    summarise(Unique = n_distinct(record))

@@

In 2012, the NIH established the Big Data to Knowledge (BD2K) initiative, recognizing the potential of data to advance our understanding of human health and disease.  This initiative was designed to support four broad goals:  1) to facilitate use of biomedical digital assets by making them discoverable, accessible, and citable; 2) to conduct research and develop methods, software and tools to analyze biomedical big data; 3) to enhance training in the development of use and tools necessary for biomedical big data science; and 4) to support a data ecosystem that accelerates discovery as part of the digital enterprise (NIH).  At roughly the same time, the National Science Foundation (NSF) created new initiatives to harness the potential of the data revolution, arguing that "data are motivating a profound transformation in the culture and conduct of scientific research in every field of science and engineering ... American scientists must rise to the challenges and seize the opportunities afforded by this new, data-driven revolution" (Suresh, XXX).  The programs of the NSF are organized around capacity building and innovative applications.  Capacity building activities focus on developing fundamental theories, techniques, methodologies and technologies that are broadly applicable to big data problems.  Innovative applications relate to specific domains advancing innovative ideas that provide solutions “with potential for a broader impact on data science and its applications.”

@@

Many journals from allied health disciplines used one of the supplemental search terms in special editions, which were also included in the journal title.  Thus, many non-social work journals were captured in the extraction process.  To resolve this issue, we created a list of all journal titles that were not part of the core list defined by Hodge and Lacasse (2011).  Study authors reviewed these journal titles and discussed whether each candidate title should be retained or excluded.  When disagreements occurred, the study authors reviewed the mission and aims of the journals, names of editorial board members, and focus of the articles.  A consensus was reached on all journal titles to be excluded and retained.   After these procedures, the number of article records and journal titles was reduced to `r pretty(nrow(article.count.journalsCleaned))` and `r journal.count.journalsCleaned`.
